%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\input{particulars}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}



\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\describe}[2]{
    \csname #1@#2\endcsname
}


\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\titlesection{
\begin{center}
    {\Huge \scshape Gangu Sasi Sekharan Sadaram} \\ \vspace{1pt}
    \small 
    \raisebox{-0.1\height}\faPhone\ +91 99025 31555 ~ \href{mailto:\email}{\raisebox{-0.2\height}\faEnvelope\  sekharan1009@gmail.com} 
    \href{\linkedin}{\raisebox{-0.2\height}\faLinkedin\ https://www.linkedin.com/in/gangu-sasi-sekharan-sadaram/} 

    \vspace{1pt}
    \href{\github}{\raisebox{-0.2\height}\faGithub\ \underline{\https://github.com/GanguSasiSekharan}}

    \vspace{1pt}
    \href{\ORCID}{\raisebox{-0.2\height}\faORCID Data-Camp
    \underline{\https://www.datacamp.com/portfolio/sekharan1009}}

    \vspace{1pt}
    \href{\ORCID}{\raisebox{-0.2\height}\faORCID ORCID
    \underline{\https://orcid.org/0000-0003-2745-4646}}
    \vspace{-8pt}
\end{center}
}

\begin{document}
\titlesection
\profileSummary

\vspace{-10pt}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading{National Institute of Technology, Karnataka - Surathkal}
      {07/2018 \ -- 04/2022}
      {Completed Bachelors in Mechanical Engineering, B.Tech}{}
 \vspace{-5pt}

      \resumeSubheading{FIITJEE Junior College - Visakhapatnam}
      {04/2016 \ -- 04/2018}
      {Completed Intermediate time (10+2), and prepared for IIT-JEE}{}
\vspace{-5pt}
      
      \resumeSubheading{Timpamy School}
      {04/2010 \ -- 03/2016}
      {Completed school time here (until 10th Std)}{}
  \resumeSubHeadingListEnd

\newcommand{\renderExp}[1]{
\resumeSubheading
      {\csname #1@Company\endcsname}{\csname #1@Start\endcsname -- \csname #1@End\endcsname}
      {\csname #1@Designation\endcsname}{\csname #1@Location\endcsname}
      \csname #1@Highlights\endcsname
}

\vspace{-10pt}

\section{Professional Experience}
    \resumeSubHeadingListStart
      \resumeSubheading{\textbf{Hong Kong and Shanghai Banking Corporation}}{07/2022 -- Present}
      {HSBC UK Remediation - Analyst - Business Consulting} {Bangalore, Karnataka, India}
      \vspace{1pt}
             
      Successfully automated numerous manual verification processes by developing pipelines with tools such as SAS and SQL, significantly accelerating redress by eliminating manual checks. 
    \resumeSubHeadingListEnd
% \vspace{-16pt}

\vspace{-10pt}
        \resumeSubheading{\textit{Tracing Customers address details}}
        {09/2023 \ -- 12/2023}{}{}
        \vspace{-18pt}
        \begin{itemize}
            \item Simplified the logic to receive the correct address of customers by developing a data pipeline.
            \vspace{-6pt}
            \item Deployed to trace back the customers who are either having incorrect address details or haven't updated their address details for a long time.
        \end{itemize}
        \vspace{-5pt}
        
        \resumeSubheading{\textit{CSEM Module and File-watcher}}
        {08/2023 \ -- 05/2024} {}{}
        \vspace{-18pt}
        \begin{itemize}
            \item Engineered an ETL pipeline to automate monthly raw data refresh; enhanced data accuracy by 99 percent and saved 30 hours of manual processing each month.
            \vspace{-6pt}
            \item Analyzed and processed raw data, extracting key markers and associated customer numbers, resulting in a 25 percent increase in data accuracy and reducing processing time by 30 percent.
            \vspace{-6pt}
            \item Implemented rigorous verification processes for customers exiting the bank, defaulting on loans, or flagged for fraud, which reduced financial risk exposure by 20 percent and improved compliance ratings.
        \end{itemize}
        \vspace{-5pt}
        
        \resumeSubheading{\textit{Sanctions File-watcher and load}}
        {01/2024 \ -- 04/2024} {}{}
        \vspace{-18pt}
        \begin{itemize}
            \item Constructed an advanced ETL pipeline for automating the weekly ingestion of sanctioned customers list; accelerated data handling by 55 percent and minimized potential compliance risks by 20 percent.
            \vspace{-6pt}
            \item Screened and blocked 150+ high-risk accounts using sanctioned list criteria; forwarded flagged accounts to the Sanctions team for further investigation, enhancing compliance and safeguarding company interests.
            \vspace{-6pt}
            \item Executed thorough screening processes to identify customers sanctioned by the UK Government or flagged by the Bank for Financial Crime, enhancing compliance by 20 percent.
        \end{itemize}

\vspace{-13pt}
\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\vspace{-2pt}
\resumeSubheading{Programming}{}{}{}
{\location{Experienced:}}{} 
SAS \textbullet{} 
Teradata SQL \textbullet{} 
MySQL \textbullet{} 
Oracle SQL \textbullet{} 
Python \textbullet{}
Microsoft Excel \textbullet{}  \\
\vspace{1pt}
{\location{Familiar:}}{}
JAVA \textbullet{} 
C \textbullet{} 
C++ \textbullet{} 
GCP \textbullet{}
BigQuery \textbullet{}
Origin Labs \textbullet{}
CATIA \textbullet{}
AutoCAD \textbullet{}
Fusion 360 \textbullet{}
Power BI \textbullet{}\\
\sectionspace


\resumeSubheading{Tools/Applications}{}{}{}
Visual Studio \textbullet{} 
GIT-Hub \textbullet{} 
Jupyter Notebook \textbullet{} 
ANACONDA \textbullet{}
MATLAB \textbullet{}
ANSYS \textbullet{}
Canva \textbullet{}
\sectionspace

\resumeSubheading{Operating Systems}{}{}{}
Windows \textbullet{} 
Linux - Ubuntu
\sectionspace

\vspace{-13pt}

\section{Internship Experience}
\resumeSubHeadingListStart
      \resumeSubheading{\textbf{NMCAD Lab \-- IISc Bangalore} $|$ Research Intern}
      {03/2021 \ -- 05/2022}{Work from Home \-- COVID}
      
      \begin{itemize}
          \item Topic - Additive Manufacturing of Auxetic Materials.
          \vspace{-2pt}
          \item Modeled 4 Auxetic Structures.
          \vspace{-2pt}
          \item Analyzed and visualized experimental data using Origin Labs Plotter, collaborating with AMTF Lab, IIT-Bombay; provided actionable insights that increased research accuracy by 25 percent and accelerated project timelines by 15 percent.
      \end{itemize} 
      \vspace{-5pt}

      \resumeSubheading{\textbf{Abyom SpaceTech and Defence Pvt. Ltd.} $|$ Research Intern}
      {06/2021 \ -- 09/2021}{Work from Home \-- COVID}
      
      \begin{itemize}
          \item Studied more about research methods and review paper writing.
          \vspace{-2pt}
          \item Wrote a review paper on the role of polymer based materials for aerospace applications.
      \end{itemize}
      \vspace{-2pt}
      
      \resumeSubheading{\textbf{Visakhapatnam Port Authority} $|$ Industrial Trainee}
      {02/2021 \ -- 03/2021}{Visakhapatnam, Andhra Pradesh, India}
      
      \begin{itemize}
          \item MV Section: Learned about the vehicles of BS3-Standard.
          \vspace{-2pt}
          \item MC Section: Studied on Fog Machine, Fork Lift(10T, 3.5T).
          \vspace{-2pt}
          \item Workshop: Learned more about Lathe Machine, different Machining Operations, Basics of Welding.
      \end{itemize}
      \vspace{-2pt}
      
      \resumeSubheading{\textbf{Space Technology and Aeronautical Rocketry} $|$ Design Intern}
      {11/2020 \ -- 12/2020}{Virtual Internship}
      
      \begin{itemize}
          \item Studied more about 3D modeling in model rocket design.
          \vspace{-2pt}
          \item Designed the Rocket Mount for the Model Rocket Static Test Pad, and the Recovery System(Parachutes) and Avionics Bay for the High-Powered Rocket.
      \end{itemize}
      \vspace{1pt}
\resumeSubHeadingListEnd

\newcommand{\renderHck}[1]{
      \resumeProjectHeading
      {\textbf{\csname #1@Title\endcsname} $|$ \csname #1@Position\endcsname}
      {\csname #1@Date\endcsname}
      \csname #1@Highlights\endcsname
}

\vspace{-15pt}
\section{College Achievements}

        \resumeSubheading{Mars Rover \ -- Team Zephyr}
        {08/2021 \ -- 03/2022}{}{}
        Team Captain | Qualified in the preliminary design review, in the University Rover Challenge 2022, conducted by the Mars Society.
        \vspace{2pt}
        
        \resumeSubheading{Drona UAV \ -- Team Aeros}
        {03/2021 \ -- 05/2021} {}{}
        Mechanical Engineer | Achieved fourth place out of 26 teams, in IPAS Challenge 2021, Mars
        Society South Asia Branch.
        \vspace{2pt}
        
        \resumeSubheading{Design of Construct-o-Bot}
        {11/2019 \ -- 02/2020} {}{}
        Team lead / Designer | Led team of four overseeing all aspects of the design and testing of the Bot; done as part of the E-Yantra 2019-2020 robotics competition, conducted by IIT-Bombay.

\vspace{-5pt}
\section{Publications}
\vspace{-5pt}
\resumeSubHeadingListStart

\vspace{5pt}

      \resumeSubheading {21-12-2022 | \textit{Journal of Thermoplastic Composite Materials} }{}{}{}\vspace{-15pt}
      
      \textbf{Experimental investigation of the in-plane quasi-static mechanical behaviour of additively manufactured polyethylene tere-phthalate or
organically modified mont-morillonite nanoclay
composite auxetic structures}

      \vspace{1pt}
      Author(s): Vinyas Mahesh, Prasad Maladkar, Gangu SS
Sadaram(Me), Athul Joseph, Vishwas Mahesh,
Dineshkumar Harursampath
      \vspace{1pt}

      \resumeSubheading {30-11-2022 | \textit{IEOM Society International} }{}{}{}\vspace{-25pt}
      \textbf{Active Vibration Control of Viscoelastic Core Sandwich Using PID, LQR and LQG Controllers} 
      
      \vspace{25pt}
      
      Author(s): Giridhar Ippili, Gangu Sasi Sekharan Sadaram(Me), Pappu Mouli, Rachana Ellur, Nagiredla Suryarao, Hemantha Kumar, Sharnappa Joladarashi  }
      
      \textbf{Active Vibration Control of MR Fluid Core Sandwich Using PID, LQR and LQG Controllers }     
      Author(s): Giridhar Ippili, Gangu Sasi Sekharan Sadaram(Me), Pappu Mouli, Rachana Ellur, Nagiredla Suryarao, Hemantha Kumar, Sharnappa Joladarashi  }
      \vspace{10pt}
    
\resumeSubHeadingListEnd


\end{document}
